The Concurrent Calculi Formalisation Benchmark

### 2024-04-10 challenges/linearity.tex
Fix minor textual issues.

Typing contexts gather type information about names and variables.
\emph{Unrestricted} contexts are simply sets of names since we only
have one base type. \emph{Linear contexts} associate a type to
endpoints. We use the comma as split/union, overloaded to singletons,
and \( \Cempty \) as the empty context. We extend the Barendregt
convention~\cite{Barendregt1984} to contexts, so that all entries are
distinct.  Note that the order in which information is added to a type
context does not matter. We denote with $\tend\Delta$ a (linear)
context whose names have all type $\Tend$.

@@

To prove that process equivalence preserves typing, it is convenient to first consider 
 the smalleset relation closed under the six axioms of
 structural congruence, denoted by $\sconga\cdot\cdot$:

>>>>

Typing contexts gather type information about names and variables.
\emph{Unrestricted} contexts are simply sets of names since we only
have one base type. \emph{Linear contexts} associate a type to
endpoints. We use the comma as split/union, overloaded to singletons,
and \( \Cempty \) as the empty context. We extend the Barendregt
convention~\cite{Barendregt1984} to contexts, so that all entries are
distinct.  Note that the order in which information is added to a type
context does not matter. We denote with $\tend\Delta$ a (linear)
context whose names all have type $\Tend$.

@@

To prove that process equivalence preserves typing, it is convenient to first consider 
 the smallest relation closed under the six axioms of
 structural congruence, denoted by $\sconga\cdot\cdot$:

### 2024-04-10 challenges/scope-extrusion.tex
Fix minor textual issues.

\subsubsection{Challenge.}
As in the linearity challence,  we first consider 
 the smalleset relation closed under the six axioms of
 structural congruence, denoted by $\sconga\cdot\cdot$:
\begin{lemma}\label{se-lemma-harmony-facta}
  If \( \sconga{P}{Q} \) and \( \transition{P}{\alpha}{P'} \), then for some \( Q' \) we have \( \transition{Q}{\alpha}{Q'} \) and \( \sconga{P'}{Q'} \).
\end{lemma}
\begin{proof}[Sketch]
By case analysis on the first derivation.
\end{proof}
\begin{lemma}\label{se-lemma-harmony-fact}
  If \( \scong{P}{Q} \) and \( \transition{P}{\alpha}{P'} \), then for some \( Q' \) we have \( \transition{Q}{\alpha}{Q'} \) and \( \scong{P'}{Q'} \).
\end{lemma}
\begin{proof}[Sketch]
    By induction on the structure of the derivation of \( \scong{P}{Q} \), with an inner induction of the structure of a process context and an appeal to Lemma~\ref{se-lemma-harmony-facta}.
\end{proof}

>>>>

\subsubsection{Challenge.}
As in the linearity challence,  we first consider 
 the smalleset relation closed under the six axioms of
 structural congruence, denoted by $\sconga\cdot\cdot$:
\begin{lemma}\label{se-lemma-harmony-facta}
  If \( \sconga{P}{Q} \) and \( \transition{P}{\alpha}{P'} \), then for some \( Q' \) we have \( \transition{Q}{\alpha}{Q'} \) and \( \sconga{P'}{Q'} \).
\end{lemma}
\begin{proof}[Sketch]
By case analysis on the first derivation.
\end{proof}
\begin{lemma}\label{se-lemma-harmony-fact}
  If \( \scong{P}{Q} \) and \( \transition{P}{\alpha}{P'} \), then for some \( Q' \) we have \( \transition{Q}{\alpha}{Q'} \) and \( \scong{P'}{Q'} \).
\end{lemma}
\begin{proof}[Sketch]
    By induction on the structure of the derivation of \( \scong{P}{Q} \), with an inner induction on the structure of a process context and an appeal to Lemma~\ref{se-lemma-harmony-facta}.
\end{proof}

### 2024-04-10 short-paper/short-paper.tex
Fix minor textual issues.

While many proof assistants support coinductive techniques, they do so
through different formalisms.
Some systems even offer multiple abstractions for utilising coinduction.
For instance, Agda offers musical notation, co-patterns and sized types~\cite{Abel2013};
Coq features guarded recursion and refined fixed point approaches via the parameterised coinduction~\cite{Hur2013}
and interaction tree~\cite{Xia2019} libraries.

>>>>

% AM <-- review
While many proof assistants support coinductive techniques, they do so
through different formalisms.
Some systems even offer multiple abstractions for utilising coinduction.
For instance, Agda offers musical notation, co-patterns and productivity checking via sized types~\cite{Abel2013};
Coq features guarded recursion and refined fixed point approaches via libraries for \eg parameterised coinduction~\cite{Hur2013}, coinduction up-to~\cite{Pous16} and interaction trees~\cite{Xia2019}.
